---
title: "example_workflow_cloud2xsample"
author: "Jacob Strunk"
date: "5/20/2020"
output: html_document
---

#install packages (only run 1 time, or when package is updated)
#installing dependencies takes a little while for some reason
#alternatively, you can download the github repository, zip it, and then use R to load package from zip file

#notice this chunk is turned off by default!! Only run one time

```{r, eval=FALSE}

	devtools::install_github("jstrunk001/CloudSampleR")

```


#load required packages
```{r }
	library(rgdal)
	library(rgeos)
	library(cloudSampleR)

```

#This is also turned off
#you only want to run this one time as well

```{r, eval=FALSE}

	tifs = list.files("D:\\data\\wa\\wadnr_hood_canal\\hood_canal_dtm",pattern="[.]tif",full.names=T)
	gdalUtils::gdalbuildvrt(tifs,"D:\\data\\wadnr_hood_canal\\hood_canal_dtm\\dtm_demo.vrt")

```

# Read in data extents (e.g. tile index shapefile) for two point clouds
```{r }

	poly1=rgdal::readOGR("D:/data/wa/wadnr_hood_canal/las/hood_canal_3in_DSM_2015/manage_las","las_polys")
	poly1a=rgeos::gBuffer(poly1,width = 5)
	poly2=rgdal::readOGR("D:/data/wa/wadnr_hood_canal/las/hood_canal_6in_DSM_2015/manage_las","las_polys")
	poly2a=rgeos::gBuffer(poly2,width = 5)

```


# Approach #1 

```{r }
	cloud2xSample(
		pathClipData = "c:/fusion/clipdata.exe"
		,pathOutA = "d:/temp/hood_canal_test/clip3in/"
		,pathOutB = "d:/temp/hood_canal_test/clip6in/"
		,pathLasA = "D:/data/wa/wadnr_hood_canal/las/hood_canal_3in_DSM_2015/"
		,pathLasB = "D:/data/wa/wadnr_hood_canal/las/hood_canal_6in_DSM_2015/"
		,extentPolyA = poly1a
		,extentPolyB = poly2a
		,nCore = 3
		,nSample = 150
		#,procMethod = "FUSION"
		,procMethod = "lidR"
		,radii = list( feet = c(FtTenthAc = 37.2, FtAcre = 117.8, Ft5Acres = 263.3 ))
		#,radii = list( feet = c(FtTenthAc = 37.2 ))
	)

```


# Approach #3 -> pass our own sample points
 -build our own sample locations
 -program buffers them
 -clip

```{r }

	library(sp)
  set.seed(35)
	samp50 = spsample(poly1a,50,type="hexagonal")
	samp50df = SpatialPointsDataFrame(samp50,data.frame(ID=1:length(samp50),project="HoodCanal3in"))
	plot(poly1a)
  plot(samp50df,add=T)
  rgdal::writeOGR(samp50df, dsn = "c:/temp" , layer="HC_samp50pts",driver="ESRI Shapefile", overwrite_layer = T, morphToESRI= T)
  
	#single buffer and bring in existing points - process with R
	cloud2xSample(
		pathClipData = "c:/fusion/clipdata.exe"
		,pathOutA = "d:/temp/hood_canal_test/clip3in/"
		,pathOutB = "d:/temp/hood_canal_test/clip6in/"
		,pathLasA = "D:/data/wadnr_hood_canal/las/hood_canal_3in_DSM_2015/"
		,pathLasB = "D:/data/wadnr_hood_canal/las/hood_canal_6in_DSM_2015/"
		,extentPolyA = poly1a
		,extentPolyB = poly2a
		,nCore = 3
		,nSample = 150
		,procMethod = "lidR"
		,radii = list( feet = c(FtTenthAc = 37.2 ))
		,sampleShpA = "c:\\temp\\HC_samp50pts.shp"
	)


```

# Approach #3 -> pass our own polygons
 -build our own sample locations
 -buffer them
 -clip

 -set sampleShape = "userPoly" otherwise the provided polygons will be buffered
```{r }

	library(sp)
  set.seed(80)
	samp50 = spsample(poly1a,50,type="hexagonal")
	samp50df = SpatialPointsDataFrame(samp50,data.frame(ID=1:length(samp50),project="HoodCanal3in"))
	samp50df_bfr100 = rgeos::gBuffer(samp50df,width=30,byid=T)
	plot(poly1a)
  plot(samp50df,add=T)
  plot(samp50df_bfr100,add=T)
  rgdal::writeOGR(samp50df_bfr100, dsn = "c:/temp" , layer="HC_samp50_bfr100",driver="ESRI Shapefile", overwrite_layer = T, morphToESRI= T)
  
	#single buffer and bring in existing points - process with R
	cloud2xSample(
		pathClipData = "c:/fusion/clipdata.exe"
		,pathOutA = "d:/temp/hood_canal_test/clip3in/"
		,pathOutB = "d:/temp/hood_canal_test/clip6in/"
		,pathLasA = "D:/data/wa/wadnr_hood_canal/las/hood_canal_3in_DSM_2015/"
		,pathLasB = "D:/data/wa/wadnr_hood_canal/las/hood_canal_6in_DSM_2015/"
		,extentPolyA = poly1a
		,extentPolyB = poly2a
		,nCore = 3
		,nSample = 150
		,procMethod = "lidR"
		#,radii = list( feet = c(FtTenthAc = 37.2 ))
		,sampleShpA = "c:\\temp\\HC_samp50_bfr100.shp"
		,sampleShape = "circle"# "userPoly"
		,proj4A = "+proj=utm +zone=10 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
    ,proj4B = "+proj=utm +zone=10 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
  
	)


```

# Approach #4 -> subtract ground
 -build our own sample locations
 -buffer them
 -clip
 -subtract ground
 
 -set sampleShape = "userPoly" otherwise the provided polygons will be buffered
```{r }

	library(sp)
  set.seed(80)
	samp50 = spsample(poly1a,50,type="hexagonal")
	samp50df = SpatialPointsDataFrame(samp50,data.frame(ID=1:length(samp50),project="HoodCanal3in"))
	samp50df_bfr100 = rgeos::gBuffer(samp50df,width=30,byid=T)
	plot(poly1a)
  plot(samp50df,add=T)
  plot(samp50df_bfr100,add=T)
  rgdal::writeOGR(samp50df_bfr100, dsn = "c:/temp" , layer="HC_samp50_bfr100",driver="ESRI Shapefile", overwrite_layer = T, morphToESRI= T)
  
	#single buffer and bring in existing points - process with R
	cloud2xSample(
		pathClipData = "c:/fusion/clipdata.exe"
		,pathOutA = "d:/temp/hood_canal_test/clip3in/"
		,pathOutB = "d:/temp/hood_canal_test/clip6in/"
		,pathLasA = "D:/data/wa/wadnr_hood_canal/las/hood_canal_3in_DSM_2015/"
		,pathLasB = "D:/data/wa/wadnr_hood_canal/las/hood_canal_6in_DSM_2015/"
		,pathDTMA = "D:\\data\\WA\\wadnr_hood_canal\\hood_canal_dtm\\hood_canal_dtm.vrt"
		,pathDTMB = "D:\\data\\WA\\wadnr_hood_canal\\hood_canal_dtm\\hood_canal_dtm.vrt"
		,extentPolyA = poly1a
		,extentPolyB = poly2a
		,nCore = 3
		,nSample = 150
		,procMethod = "lidR"
		#,radii = list( feet = c(FtTenthAc = 37.2 ))
		,sampleShpA = "c:\\temp\\HC_samp50_bfr100.shp"
		,sampleShape = "circle"# "userPoly"
		,proj4A = "+proj=utm +zone=10 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
    ,proj4B = "+proj=utm +zone=10 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
  
	)


```


# Approach #5 -> speedup with lax indices
 -buld lastools lax indices
 -build our own sample locations
 -buffer them
 -clip
 -subtract ground
 
 ##Note the native lastools function lasindex/lasindex64 is !MUCH! faster than lidR:::catalog_laxindex(...)
 ## - yes that is a triple colon (:::) - catalog_laxindex is not an exported function, we have to get fancy to access the hidden function
 -set sampleShape = "userPoly" otherwise the provided polygons will be buffered
```{r }


	#only run once, very slow
	if(!file.exists("d:/data/WA/wadnr_hood_canal/las/hood_canal_12in_DSM_2015/area1_000_000.0_6.lax")){
		library(future)
		shell("C:\\lastools\\LAStools\\bin\\lasindex64 -i d:\\data\\WA\\wadnr_hood_canal\\las\\hood_canal_12in_DSM_2015\\*.las -cores 4 -dont_reindex", wait=T)
	}
  	#only run once, very slow
	if(!file.exists("d:/data/WA/wadnr_hood_canal/las/hood_canal_6in_DSM_2015/area1_000_000.0_6.lax")){
		shell("C:\\lastools\\LAStools\\bin\\lasindex64 -i d:\\data\\WA\\wadnr_hood_canal\\las\\hood_canal_6in_DSM_2015\\*.las -cores 4 -dont_reindex", wait=T)
	}
  	#only run once, very slow
	if(!file.exists("d:/data/WA/wadnr_hood_canal/las/hood_canal_3in_DSM_2015/Sub_Area_000_000.9_6.lax")){
		shell("C:\\lastools\\LAStools\\bin\\lasindex64 -i d:\\data\\WA\\wadnr_hood_canal\\las\\hood_canal_3in_DSM_2015\\*.las -cores 4 -dont_reindex", wait=T)
	}
	library(sp)
  set.seed(80)
	samp50 = spsample(poly1a,50,type="hexagonal")
	samp50df = SpatialPointsDataFrame(samp50,data.frame(ID=1:length(samp50),project="HoodCanal3in"))
	samp50df_bfr100 = rgeos::gBuffer(samp50df,width=30,byid=T)
	plot(poly1a)
  plot(samp50df,add=T)
  plot(samp50df_bfr100,add=T)
  rgdal::writeOGR(samp50df_bfr100, dsn = "c:/temp" , layer="HC_samp50_bfr100",driver="ESRI Shapefile", overwrite_layer = T, morphToESRI= T)
  
	#single buffer and bring in existing points - process with R
	cloud2xSample(
		pathClipData = "c:/fusion/clipdata.exe"
		,pathOutA = "d:/temp/hood_canal_test/clip12in/"
		,pathOutB = "d:/temp/hood_canal_test/clip3in/"
		,pathLasA = "d:/data/WA/wadnr_hood_canal/las/hood_canal_12in_DSM_2015"
		,pathLasB = "D:/data/wa/wadnr_hood_canal/las/hood_canal_3in_DSM_2015/"
		,pathDTMA = "D:\\data\\WA\\wadnr_hood_canal\\hood_canal_dtm\\hood_canal_dtm.vrt"
		,pathDTMB = "D:\\data\\WA\\wadnr_hood_canal\\hood_canal_dtm\\hood_canal_dtm.vrt"
		,extentPolyA = poly1a
		,extentPolyB = poly2a
		,nCore = 3
		,nSample = 150
		,procMethod = "lidR"
		#,radii = list( feet = c(FtTenthAc = 37.2 ))
		,sampleShpA = "c:\\temp\\HC_samp50_bfr100.shp"
		,sampleShape = "circle"# "userPoly"
		,proj4A = "+proj=utm +zone=10 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
    ,proj4B = "+proj=utm +zone=10 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
  
	)


```



# Approach #6 incorporate projection differences (different dataset), clip slices instead
 -buld lastools lax indices
 -build our own sample locations
 -buffer them
 -clip
 -subtract ground
 
```{r }

	library(lidR)
	library(cloudSampleR)

  dir_proj = "D:\\Box\\VMARS\\Projects\\DAP_evaluation_Meston"
	dir_tn_dat = file.path(dir_proj,"Data\\Tennessee")
	dir_tn_las = file.path(dir_proj,"Data\\Tennessee\\lidar_tiles")
	dir_tn_dap = file.path(dir_proj,"Data\\Tennessee\\dap_tiles")
	dir_tn_dtm_las = file.path(dir_proj,"Data\\Tennessee\\dtm")
	dir_tn_dtm_dap = file.path(dir_proj,"Data\\Tennessee\\dtm_dap")
	
	#prepare lidar data
	files_tn_las = list.files(dir_tn_las,pattern="[.]laz",full.names=T,recursive=T)
	ctg_tn_las <- lidR::readLAScatalog(files_tn_las)
	ctg_tn_las
	plot(ctg_tn_las)
	sp::proj4string(ctg_tn_las)
	ply_tn_las = SpatialPolygons(ctg_tn_las@polygons)
  df_ply_tn_las = SpatialPolygonsDataFrame(ply_tn_las,data.frame(files_tn_las))
  border_las = buffer(df_ply_tn_las,5)
  
  #prepare dap data
	files_tn_dap = list.files(dir_tn_dap,pattern="[.]laz",full.names=T,recursive=T)
	ctg_tn_dap <- lidR::readLAScatalog(files_tn_dap)
	ctg_tn_dap
	raster::plot(ctg_tn_dap)
	sp::proj4string(ctg_tn_dap)
	
	#extract polygon of tile extents
	ply_tn_dap = SpatialPolygons(ctg_tn_dap@polygons)
	df_ply_tn_dap = SpatialPolygonsDataFrame(ply_tn_dap,data.frame(files_tn_dap))
	border_dap = buffer(df_ply_tn_dap,5)
		
	#fix bad proj4 string - correct zone is 16 NOT zone 19 ....
	proj4string(df_ply_tn_dap) = "+proj=utm +zone=16 +ellps=GRS80 +units=m +no_defs"
	
	#sample lidar strips
	set.seed(55)
	samp_pts_tn = sp::spsample(ply_tn_las,100,"random")
	
	#build sample strips polygons - these are in the same projection as ctg_tn_las, the lidar data
	xoff = 50
	yoff = 2
	strip_0 = SpatialPolygons(list(Polygons(list(Polygon(data.frame(x=c(-xoff,xoff,xoff,-xoff,-xoff),y=c(-yoff,-yoff,yoff,yoff,-yoff)))) , ID = 1)))
	cds_samp = sp::coordinates(samp_pts_tn)
	samp_strips = do.call(bind,mapply( raster::shift , dx=cds_samp[,1] , dy = cds_samp[,2] , MoreArgs = list(x=strip_0) ))
	samp_strips_df = SpatialPolygonsDataFrame(samp_strips, data = data.frame(ID=1:nrow(cds_samp),cds_samp), match.ID = F)
  plot(samp_strips_df,lwd=5,border="Red")
  proj4string(samp_strips_df) = sp::proj4string(ctg_tn_dap)
  rgdal::writeOGR(samp_strips_df, dsn="D:\\Box\\VMARS\\Projects\\DAP_evaluation_Meston\\R\\DAP_Lidar_analysis\\data",layer="tn_samp_ply.shp",driver="ESRI Shapefile",overwrite_layer = T)
  
  #build .vrt for lidar dtms - a virtual mosaic so that we can poitn to a single file
  files_dtm_tn_las = list.files(dir_tn_dtm_las , pattern="[.]img",full.names=T,recursive=T)
	out_dtm_tn_las = file.path(dir_tn_dtm_las,"tn_dtm.vrt")
	if(!file.exists(out_dtm_tn_las)) gdalUtils::gdalbuildvrt( files_dtm_tn_las , out_dtm_tn_las)
  
  #reproject lidar dtms to match DAP projection
	try(dir.create(dirname(out_dtm_tn_dap)))
  las_dtm = raster::raster(out_dtm_tn_las)
  for(i in 1:length(files_dtm_tn_las)){
  	rasteri = raster::raster(files_dtm_tn_las[[i]])
  	outi = file.path(dir_proj,"Data\\Tennessee\\DTM_dap",basename(files_dtm_tn_las[[i]]))
  	if(!file.exists(outi))raster::projectRaster(from = rasteri, crs= CRS("+proj=utm +zone=16 +ellps=GRS80 +units=m +no_defs") , filename = outi)
  }

  #build .vrt for dap dtms - a virtual mosaic so that we can poitn to a single file
  files_dtm_tn_dap = list.files(dir_tn_dtm_dap , pattern="[.]img$",full.names=T)
  out_dtm_tn_dap = file.path(dir_proj,"Data\\Tennessee\\DTM_dap\\tn_dtm_dap.vrt")
	if(!file.exists(out_dtm_tn_dap)) gdalUtils::gdalbuildvrt( files_dtm_tn_dap, out_dtm_tn_dap)
  
	#single buffer and bring in existing points - process with R
	cloud2xSample(
		pathClipData = "c:/fusion/clipdata.exe"
		,pathOutA = "d:/temp/tennessee/clip_las/"
		,pathOutB = "d:/temp/tennessee/clip_dap/"
		,pathLasA = dir_tn_las
		,pathLasB = dir_tn_dap
		,pathDTMA = out_dtm_tn_las
		,pathDTMB = out_dtm_tn_dap
		,extentPolyA = border_las
		,extentPolyB = border_dap
		,nCore = 3
		#,nSample = 100 #not used when argument is provided to sampleShpA
		,procMethod = "lidR"
		#,radii = list( feet = c(FtTenthAc = 37.2 )) #not used when sampleShape = "userPoly"
		,sampleShpA = "D:\\Box\\VMARS\\Projects\\DAP_evaluation_Meston\\R\\DAP_Lidar_analysis\\data\\tn_samp_ply.shp"
		,sampleShape = "userPoly"
		,proj4A = 
			"+proj=lcc +lat_1=36.41666666666666 +lat_2=35.25 +lat_0=34.33333333333334 +lon_0=-86 +x_0=600000 +y_0=0 +ellps=GRS80 +units=us-ft +vunits=us-ft +no_defs"
    ,proj4B = "+proj=utm +zone=16 +ellps=GRS80 +units=m +no_defs"
  
	)


```
